Analysis

### 2023-05-03 analysis/analysis.Rmd
Replace neotoma with neotoma2
Which is now on CRAN

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(ggspatial)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
library(grid)
```

@@

```{r message=FALSE}
if(!require('devtools')) install.packages('devtools')
library(devtools)
install_github('ISAAKiel/aoristAAR')
require(aoristAAR)
```
Also, neotoma is not longer available on cran, and it has been replaced by neotoma2, so we had to replace it. That is why we have to load it again:

```{r}
if(!require('neotoma2')) devtools::install_github('NeotomaDB/neotoma2')
require(neotoma2)
```

>>>>

```{r message=FALSE}
library(analogue)
library(coda)
library(doParallel)
library(fmcmc)
library(ggdist)
library(ggspatial)
library(grid)
library(here)
library(MCMCvis)
library(neotoma2)
library(nimble)
library(rcarbon)
library(RcppRoll)
library(reshape2)
library(sf)
library(tidyverse)
library(vegan)
```

@@

```{r message=FALSE}
if(!require('devtools')) install.packages('devtools')
library(devtools)
install_github('ISAAKiel/aoristAAR')
require(aoristAAR)
```
